### 2020-09-03 latex/vlp.tex
added more TODOs and figured out what to do with images

@@

The time-optimal controller described by \cite{pumping_swing_standing_squatting}
depends on a state trajectory in time. We will convert this time-based
controller into a time-independent controller which still uses this time-optimal
strategy. Notice that the control strategy depends on knowing when the
system is at the ``bottom" or ``top" of the swing. Since being at the ``bottom"
is the same as saying the pendulum angle is \(q = 0\) and being at the ``top" is
equivalent to the pendulum's momentum being \(p = 0\), our method of
VNHCs is especially well suited to this problem.

Figure \ref{fig:vlp-optimal-controller-qp-plane} shows the time-optimal strategy directly
on the \((q,p)\)-plane. The axes of this plane define where the pendulum should
change length. Since the pendulum stays the same length inside each quadrant, we
will use the angle \(\theta = \arctan_2(p,q)\) in the \((q,p)\)-plane to define
the optimal controller \(l^\star(\theta)\) (\ref{eqn:vlp-optimal-controller}).
Figure \ref{fig:vlp-optimal-controller} shows this controller as a function of
\(\theta\).
\begin{equation}\label{eqn:vlp-optimal-controller}
   l^\star(\theta):= \begin{cases}
      \underline{l} & \theta \in [-pi, -\frac{\pi}{2}[ \cup [0,\frac{\pi}{2}[ \\
      \overline{l} & \theta \in [-\frac{\pi}{2},0[ \cup [\frac{\pi}{2}, \pi[ \\
   \end{cases}
\end{equation}

\begin{figure}
   \centering
   % TODO: Inser the image of the optimal controller in the (q,p) plane
   \caption{The time-optimal VLP controller from
   \cite{pumping_swing_standing_squatting} displayed in the
\((q,p)\)-plane.}\label{fig:vlp-optimal-controller-qp-plane}
\end{figure}

\begin{figure}
   \centering
   %TODO: Insert the image of the optimal controller as a function of theta
   \caption{The time-optimal VLP controller converted to a discontinuous
   function \(l(\theta)\).}\label{fig:vlp-optimal-controller}
\end{figure}

@@

\begin{figure}
   \centering
   % TODO: Insert the image of the smoothed VLP controller
   \caption{The smoothed VLP controller attained by setting the parameter 
      \(T\) to its upper limit
   \(\frac{\pi}{2}\).}\label{fig:vlp-smoothed-controller}
\end{figure}

>>>>

% TODO: Describe the oscillation and rotation motion of a pendulum in the
% qp-plane, and give a figure showing the orbiting motion for each of these.
% Then describe what the orbit should do under energy injection (spiral away /
% begin rotation outward) and energy dissipation (spiral in / rotate inward).

@@

The time-optimal controller described by \cite{pumping_swing_standing_squatting}
depends on a trajectory in time. We will convert this 
into a time-independent controller derived from the time-optimal
strategy. Notice that the optimal controller depends on knowing when the
system is at the ``bottom" or ``top" of the swing. Since being at the ``bottom"
is the same as saying the pendulum angle is \(q = 0\) and being at the ``top" is
equivalent to the pendulum's momentum being \(p = 0\), the time-independent
controller will necessarily use the full phase \((q,p)\). While VHCs cannot
satisfy this requirement, our method of VNHCs is especially well suited to this
problem.

Figure \ref{fig:vlp-optimal-controller-qp-plane} shows the time-optimal strategy directly
on the \((q,p)\)-plane.
Since the VLP must stay the same length inside each quadrant and
changes length only when it crosses one of the axes, we
will use the angle \(\theta = \arctan_2(p,q)\) in the \((q,p)\)-plane to define
the optimal controller \(l^\star(\theta)\) (\ref{eqn:vlp-optimal-controller}).
Figure \ref{fig:vlp-optimal-controller} shows this time-optimal controller as a function of
\(\theta\).
\begin{equation}\label{eqn:vlp-optimal-controller}
   l^\star(\theta):= \begin{cases}
      \underline{l} & \theta \in [-pi, -\frac{\pi}{2}[ \cup [0,\frac{\pi}{2}[ \\
      \overline{l} & \theta \in [-\frac{\pi}{2},0[ \cup [\frac{\pi}{2}, \pi[ \\
   \end{cases}
\end{equation}

\begin{figure}
   \centering
   % TODO: Inser the image of the optimal controller in the (q,p) plane: it
   % should just be 4 coloured quadrants (no spiral) representing squatting and
   % standing
   \caption{The time-optimal VLP controller from
   \cite{pumping_swing_standing_squatting} displayed in the
\((q,p)\)-plane.}\label{fig:vlp-optimal-controller-qp-plane}
\end{figure}

\begin{figure}
   \centering
   %TODO: Insert the image of the optimal controller as a function of theta;
   %that is, show l(theta) vs theta on ]-pi,pi] and show underline{l} and
   %overline{l} 
   \caption{The time-optimal VLP controller converted to a discontinuous
   function \(l(\theta)\).}\label{fig:vlp-optimal-controller}
\end{figure}

@@

\begin{figure}
   \centering
   % TODO: Insert the image of the smoothed VLP controller around lavg
   \caption{The smoothed VLP controller attained by setting the parameter 
      \(T\) to its upper limit
   \(\frac{\pi}{2}\).}\label{fig:vlp-smoothed-controller}
\end{figure}
